Spatial Relational Models for Neural Circuit Discovery

### 2013-10-21 docs/techreport.tex
added output plots cleaned up plots for generation

@@

\subsection{Drosophila medulla}
\autocite{Takemura2013}
No cell bodies -- what to use for distance? 
Human annotation
what the hell is a cell

>>>>

\begin{figure}
  \centering 
  \includegraphics[width=0.5\textwidth]{mouseretina/adjmat.byz.png}
  \caption{Mouse connectome for the 950 cells with known soma positions, ordered by the position of the soma along the $z$ axis. The size of each point is proportional to the total area of contact between the cells.}
  \label{fig:mouse_adj}
\end{figure}

@@

279 neurons (non-phyrnx)

\begin{figure}
  \centering 
  \includegraphics[width=0.5\textwidth]{celegans/data.pos.pdf}
  \caption{Connectome for the 279 non-pharynx cells in \textit{c. elegans}. Cells are ordered by their position along the body axis. Blue dots are chemical synapses, red dots are electrical synapses, and the area of each dot is equivalent to the number of synaptic contacts between the cells. Note that the chemical synapses (blue) are directional, thus the red dots form a symmetric matrix}
  \label{fig:celegans_adj}
\end{figure}

\subsection{Drosophila medulla}
\autocite{Takemura2013}
No cell bodies -- what to use for distance? 
Human annotation
what the hell is a cell
357 cells by the time we get through it

\begin{figure}
  \centering 
  \includegraphics[width=0.5\textwidth]{drosophila/adj_comp.pdf}
  \caption{Connectome for the 357 cells in \textit{drosophila} medulla. Cells are ordered by the order they appear in the data file. Dot area is proportional to the number of synapses; data are directional.}
  \label{fig:drosophila_adj}
\end{figure}
